Sorting by Reversals

### 2020-07-12 paper.tex
update paper

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}{Example}[theorem]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

\begin{figure}
    \begin{align*}
        \pi = (7\ \mid\ 5\ 6\ \mid\ 3\ 2\ \mid\ 4\ \mid\ 1)
    \end{align*}
    \caption{Breakpoints (breakpoints marked by vertical bars)}
    \label{fig:breakpoints}
\end{figure}

@@

Using this lower bound, \citeauthor*{Bafna1996} already describe a $\frac{7}{4}$-approximation that is not considered in more detail here. \citeauthor*{Christie1998} formulated a lower bound in terms of the number of $2$-cycles in a maximum alternating cycle decomposition \cite{Christie1998}.

@@

\begin{proof}
$b(\pi)$ is the number of red edges in $G(\pi)$ and $c_2(\pi)$ is the number of red edges in $2$-cycles of $G(\pi)$. Therefore, $b(\pi) - 2 c_2(\pi)$ is the number of \textit{free} red edges in $G(\pi)$ not occurring in $2$-cycles. $3 c_{3*}(\pi)$ is a lower bound to the number of red edges in $G(\pi)$ not occurring in $2$-cycles as every such cycle has at least three constituting red edges, proving the lemma.
\end{proof}

@@

\begin{example}
Consider the alternating cycle decomposition
\begin{align*}
    \mathcal{C} = \{&(\{0,7\},\{6,7\},\{3,6\},\{3,4\},\{1,4\},\{0,1\}), \\
                    &(\{5,7\},\{4,5\},\{2,4\},\{1,2\},\{1,8\},\{7,8\})\}
\end{align*}
of the breakpoint graph of $(0\ 7\ 5\ 6\ 3\ 2\ 4\ 1\ 8)$. The corresponding reversal graph is given in figure \ref{fig:reversal_graph}.
\end{example}

@@

\begin{example}
Applying the reversal represented by vertex $\{4,5\}$ in figure \ref{fig:reversal_graph} results in the breakpoint and reversal graphs shown in figures \ref{fig:breakpoint_graph_change} and \ref{fig:reversal_graph_change} respectively.
\end{example}

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

\begin{figure}
    \begin{align*}
        (7\ \mid\ 5\ 6\ \mid\ 3\ 2\ \mid\ 4\ \mid\ 1)
    \end{align*}
    \caption{Breakpoints (breakpoints marked by vertical bars)}
    \label{fig:breakpoints}
\end{figure}

@@

Using this lower bound, \citeauthor*{Bafna1996} already describe a $7/4$-approximation that is not considered in more detail here. \citeauthor*{Christie1998} formulated a lower bound in terms of the number of $2$-cycles in a maximum alternating cycle decomposition \cite{Christie1998}.

@@

\begin{proof}
$b(\pi)$ is the number of red edges in $G(\pi)$ and $c_2(\pi)$ is the number of red edges in $2$-cycles of $G(\pi)$. Therefore, $b(\pi) - 2 c_2(\pi)$ is the number of red edges in $G(\pi)$ not occurring in $2$-cycles. $3 c_{3*}(\pi)$ is a lower bound to the number of red edges in $G(\pi)$ not occurring in $2$-cycles as every such cycle has at least three constituting red edges, proving the lemma.
\end{proof}

@@

Consider the alternating cycle decomposition
\begin{align*}
    \mathcal{C} = \{&(\{0,7\},\{6,7\},\{3,6\},\{3,4\},\{1,4\},\{0,1\}), \\
                    &(\{5,7\},\{4,5\},\{2,4\},\{1,2\},\{1,8\},\{7,8\})\}
\end{align*}
of the breakpoint graph of $(0\ 7\ 5\ 6\ 3\ 2\ 4\ 1\ 8)$. The corresponding reversal graph is given in figure \ref{fig:reversal_graph}.\padding

@@

Applying the reversal represented by vertex $\{4,5\}$ in figure \ref{fig:reversal_graph} results in the breakpoint and reversal graphs shown in figures \ref{fig:breakpoint_graph_change} and \ref{fig:reversal_graph_change} respectively.
